\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-29 paper/paper 2/dc-2015.tex
RDF-CV

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation.
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints.
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.

@@

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).

@@

Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system to formulate constraints.

@@

RDF validation and \emph{OWL 2} assume different semantics. 
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
We compare semantics of RDF validation and of \emph{OWL 2} as we consider \emph{OWL 2} as a constraint language 
when RDF validation semantics are applied.
%
\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}. 
As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
{\em Hamlet} must have at least one \emph{title} as well.
In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know ($\mathcal{K}$ is consistent).
As RDF validation has its origin in the XML world
many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
In the example, the \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}.

Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
\emph{UNA} causes a clash
if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
which resolves the violation. 
%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.

%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%%\tb{the following example does not show the redundancy problem!}
%%\tb{2. benefit: reasoning solves redundancy problem}
%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
%{\em Hamlet} must have at least one \emph{title}.
%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
%A constraint that says that a book must have at least one title in \emph{OWA}, 
%does not mean that the title has to be unique. 
%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
%it can be the case that a book has a single title, however, 
%this title is not unique. 
%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
%And since in every model there is only one, \emph{DL} sentences are satisfied. 
%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

%\begin{itemize}
%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other. We have to provide formal generic semantics for it; formally prove those statements.}

%\item This is simple. You write that:
%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it. So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated. That shows that they behave in the same way, as they should.

@@

%\item Now, what is a generic semantics? 
%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language. However, regarding CWA and OWA, it is possible that we made some mistakes. In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
%\end{itemize}

Differences in semantics may lead to differences in validation results when applied to particular constraint types.
For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.

Two constraints are identical w.r.t. RDF semantics, 
if they detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
As we use multiple languages to express constraints of constraint types, 
%in the first appendix of this paper,
we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
This is also needed to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
behave in the same way with regard to validation results which semantically underpins bidirectional mappings.

@@

A \emph{constraint language} is a language which is used to formulate constraints.
The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
As there are already five promising constraint languages, 
our purpose is not to propose a new language.
We rather developed a very simple lightweight vocabulary,
consisting of only three classes, three object properties, and three data properties, 
which is universal enough to describe constraints of any constraint type.
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
\begin{figure}
	\centering
		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
For each set of constraints, we state the rounded number of associated constraint types in brackets.
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
In case \emph{complex constraints} are expressible in \emph{DL}, 
\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
The constraints of almost 15\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

Constraints of almost 15\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of \emph{DL}.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}):

@@

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.

Constraints can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)} or specifically (\emph{specific constraint}) by domain-specific constraint languages.
Hence, we mapped constraint types to \emph{DL} 
in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.

We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).

>>>>

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints.
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.

@@

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).

@@

Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.

@@

RDF validation and \emph{OWL 2} assume different semantics. 
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
We compare semantics of RDF validation and \emph{OWL 2} as \emph{OWL 2} is considered as a constraint language 
when validation semantics is applied.
\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}. 
As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book}, %{\small\ms{(Book(Hamlet)),}}
{\em Hamlet} must have at least one \emph{title}.
In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know. 
%($\mathcal{K}$ is consistent).
As RDF validation has its origin in the XML world
many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
The \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
\emph{UNA} causes a clash
if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
which resolves the violation. 
%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%%\tb{the following example does not show the redundancy problem!}
%%\tb{2. benefit: reasoning solves redundancy problem}
%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
%{\em Hamlet} must have at least one \emph{title}.
%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
%A constraint that says that a book must have at least one title in \emph{OWA}, 
%does not mean that the title has to be unique. 
%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
%it can be the case that a book has a single title, however, 
%this title is not unique. 
%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
%And since in every model there is only one, \emph{DL} sentences are satisfied. 
%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other. We have to provide formal generic semantics for it; formally prove those statements.}
%\item This is simple. You write that:
%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it. So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated. That shows that they behave in the same way, as they should. 

@@

%\item Now, what is a generic semantics? 
%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language. However, regarding CWA and OWA, it is possible that we made some mistakes. In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
Differences in semantics may lead to differences in validation results when applied to particular constraint types.
This is important 
as for 56.8\% of the constraint types validation results differ if the \emph{CWA} or the \emph{OWA} 
and as for 66.6\% of the constraint types validation results are different in case the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.

Constraints are identical w.r.t. RDF semantics, 
if they detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
As we use multiple languages to express constraints of constraint types, 
%in the first appendix of this paper,
we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
This is also important to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.

@@

A \emph{constraint language} is a language which is used to formulate constraints.
The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
As there are already five promising constraint languages, 
our purpose was not to invent a new language.
As there is no high-level declarative language which meets all RDF validation requirements,
we rather developed a very simple lightweight vocabulary,
consisting of only three classes, three object properties, and three data properties, 
which is universal enough to describe constraints of any constraint type.
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
\begin{figure}
	\centering
		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

We classify sets of constraints according to four dimensions.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
%In the following, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
we show that constraints of any constraint type can be described generically.
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 70\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (30\%). 
%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3 of the constraint types) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
%In case \emph{complex constraints} are expressible in \emph{DL}, 
%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Constraints of almost 15\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
%Such axioms, however, are just syntactic sugar - 
%all role characteristics can be expressed using the basic features of \emph{DL}.
%
%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
%\begin{DL}
%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
%\end{DL}
%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
%
%%\begin{gcotable}
%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Complex Constraints}
	%\label{tab:irreflexive-object-properties-as-complex-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		%\end{tabular}
%\end{table}
%
%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
%
%%\begin{gcotable}
%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
%%\end{gcotable}
%
%\begin{table}[H]
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\caption{Irreflexive Object Properties as Simple Constraints}
	%\label{tab:irreflexive-object-properties-as-simple-constraints}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
%property & $\top$ & authorOf & - & - & irreflexive & - \\
		%\end{tabular}
%\end{table}
The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}):

@@

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
